Development of Performance Regression Analysis Tool using Distributed Tracing on microservice-based Application\\

### 2022-09-07 paper.tex
txs auto checkin

\documentclass[conference]{configs/IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{multirow}
%\def\tablename{Table}
%\def \figurename{Figure}

@@

\begin{abstract}
In applications with Microservice architecture, when a significant change occurs and result in decreased performance or regression, it is difficult to perform analysis to check which part of the whole Microservice is the main cause of the regression due to the distributed nature of Microservice. Distributed tracing can be used to analyze and determine whether there is a regression and the cause of the regression by utilizing latency data from existing operations on Microservice application.
This system will perform performance regression analysis using the distributed tracing tool Zipkin. Regression is then can be detected using Kolmogorov-Smirnov statistical analysis which will compare the latency data samples that occur
periodically and the sample latency baseline data that represents application performance  under normal circumstances. The analysis will compare the Cummulative
Distribution Function (CDF) of the two samples and see if both
CDF comes from a different distribution. If it is found that both CDFs originate from different distributions, it then can be suspected that there has been a performance regression because the distribution of the periodic data has deviated from the distribution of the baseline data.
If a regression is detected, the system will then perform a critical path analysis to see which operations of each services are most likely contributed to the regression. The analysis will be carried out by finding the difference
latency of periodic and baseline operation data and it will be seen which operation's latency difference exceeds a predetermined limit.
The performance regression analysis system has been tested on a Microservice application that runs on Kubernetes. The result is that out of 10 out of 11 test cases, and for every successful case, the main suspected operation that causes regression is found. Implementing the system adds an average overhead of 0.78\% CPU usage and 0.67\% Memory usage.
\end{abstract}

@@

@@

\subsection{Performance Regression Detection in DevOps}
This study \cite{regression-detection} proposes to perform regression detection performance at the DevOps stage, i.e. at the level of the source code change. The main thing considered is to avoid detecting performance regressions after the app is deployed and running in a production environment. There are two ways proposed by the research
to detect performance regressions at the DevOps stage:
\begin{enumerate}
	\item Perform regression detection at the source code level by extracting
	every Git commit and identify which test cases are affected by
	regression on each commit. After that, the performance of each commit will be
	evaluated chronologically using the relevant test cases or
	benchmarks of performance. Finally, a statistical analysis will be carried out on the performance evaluation
	to identify which changes resulted in the performance regression. To find out the root of the problem at the code level, an iterative approach will be done  to identify the root causes of
	regression until it can no longer generate new reasons.
	\item Predict which tests may manifest regression at the commit level. This approach is a continuation of the previous point where
	the approach of doing a test on every commit takes a lot
	resources and effort so that this approach will make predictions
	automatically whether a test will manifest a performance regression given a commit code. In detail, this approach will detect whether there is a regression on certain tests of a commit. To make a prediction model, it must first identified which tests are prone to yielding regression by evaluating all the tests affected by the code changes in previous commits by calculating the performance of each test, such as response time,
	CPU and Memory usage, I/O reads and writes, by doing
	each test sequentially.
\end{enumerate}

@@

There are two approaches that can be taken to solve the problem of performance regression \cite{regression-detection}, namely:
\begin{enumerate}
	\item Regression detection is carried out after the application has been developed and deployed in a dedicated environment:
	\item Regression detection is carried out before the application is developed and deployed, and then conducting a study of the resulting changes to the source code
\end{enumerate}

%Given the distributed nature of Microservices, it will be difficult for developers if regression detection is carried out with an individual approach on each existing servce especially when the number of existing servce is very large, and the interdependence relationship between services becomes complicated. Therefore, to overcome performance regression in microservice-based application, an approach that does not require developers to source search is needed. So that in the case of detection and regression analysis of microservice-based application performance, the first approach is more suitable to use.
Given the distributed nature of microservices, it will be difficult for developers if regression detection is carried out with an individual approach on each existing service espe- cially when the number of existing service is very large, and the interdependence relationship between services becomes complicated. Therefore, to overcome performance regression in microservice-based application, an approach that does not require developers to source search is needed. So that in the case of detection and regression analysis of microservice-based application performance, the first approach is more suitable to use.

Therefore, the workflow that must be carried out by the performance regression analysis (PRA) system is as follows:
\begin{enumerate}
	\item The system must be able to detect when there is a regression in microservice-based application
	\item The system must be able to determine the source or root cause of the regression after it is detected
\end{enumerate}

Seeing the needs of the PRA system above, the approach the will be carried out to do performance regression analysis will be Cummulative Analysis and Aggregation Analysis.

Cummulative Analysis is an approach to analyze certain metrics of application such as latency by cummulating all the collected data as a single representation such as Histogram. With this approach, the distributed nature of many services in microservice-based application can be observed as a single figure or representation so that the whole Microservice application can be monitored in a single space. One of the available tool to analyze and compare large sets of data is called Kolmogorov-Smirnov (K-S) statistic test. The K-S statistic test will count the difference between two Cummulative Distribution Functions (CDF) as a scalar number \cite{kolmogorov_1951}.

K-S statistic are obtained by finding the furthest vertical distance between the two CDFs as indicated by the arrows. The greater the distance, the more likely it is that two CDFs are from two different distributions so that it can be an indication that there has been a change on performance.
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.35\textwidth]{resources/ch2/ks.png}
	\caption{CDF of two samples, arrows indicate the Kolmogorov-Smirnov statistical value \cite{wiki:ks-test}}
	\label{ks-example}
\end{figure}

@@

The Cummulative Analysis approach will be used to fullfil the first needs of the PRA system by using Kolmogorov-Smirnov statistic test.

@@

Tab. \ref{aggregate} shows the result of the Aggregation Analysis approach which will be useful in determining the possible root cause of the regression. This approach will be used to fullfil the second needs of the PRA system.
\begin{table}[!htb]
	\caption{Aggregation Analysis result}
	\label{aggregate}
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		\textbf{Service/Operation} & \textbf{Baseline} & \textbf{Regression} & \textbf{Difference} \\ \hline
		inventory/write-cache & 63.1 ms & 368 ms  & +305 ms  \\ \hline
		inventory-db/update   & 1.75 ms & 2.26 ms & +0.51 ms \\ \hline
		memcached/set         & 4.94 ms & 4.71 ms & -0.23 ms \\ \hline
		inventory/update      & 15.2 ms & 14.8 ms & -0.47 ms \\ \hline
		inventory/db-update   & 32 ms   & 30.6 ms & -1.4 ms  \\ \hline
	\end{tabular}
\end{table}

Fig. \ref{flow-pra} illustrates the phases to be carried out by the PRA system. In general, there will be two phases to be carried out, namely the baseline loading phase
and the periodic analysis phase. The first phase, namely the loading phase, will look for stable application activity data that can be used as a baseline or a reference for the analysis to be carried out in the next stages. This phase
will produce two artifacts, the latency data of all recorded traces by the tracing system, and operating data that occurs on the critical path of all traces along with its latency value which will be stored as a key-value pair as well.
\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.5\textwidth,scale=5]{resources/ch3/alur_v2.png}
	\caption{PRA system workflow}
	\label{flow-pra}
\end{figure}

The next phase is the periodical analysis phase. This phase will run continuously and the analysis will be run periodically at intervals of every 5 minutes. This is carried out to continuously detect whether there is a regression and
immediately determine the source of the regression if it occurs. There are several stages of analysis
to be carried out in this phase. The first analysis stage will compare the results transformation of data latency of all ongoing traces periodically with the baseline latency artifact from the loading phase. The comparison will be made within a certain period. The comparison of the two latency data will produce Kolmogorov-Smirnov statistic. If the Kolmogorov-Smirnov statistic that is generated indicates that the two samples of latency data come from two different distributions, then it can be an indication that there has been a regression in the data capture in the periodical phase.

@@

There are two stages that will be carried out to do this experiment test, the first is baseline data collection stage. Baseline data will be taken by simulating
the usage of the application by using the Load Generator which will run with variable of \textbf{25 Users} and \textbf{5 Spawn Rates} for \textbf{1 hour}. This baseline data will then be stored by the engine for use in future test cases. The next step is to carry out experiment testing with cases which will be explained in more detail further.

There are two types of test cases to be tested on the system. Tirst type are cases that simulate regression by making changes that occurs at the application level by making modifications intentionally at the code level.
The first case will have an ID with an \textbf{SI} prefix signifying the \textit{Scenario-Internal}.
The second type are cases that simulate regression by increasing the number of users and load on the Load Generator. The second case will have an ID with the \textbf{SE} prefix denotes an \textit{Scenario-External}. Tab. \ref{testcases} will explain the cases
system testing.

@@

\subsection{Experiment Result}
The following tables \ref{test-1} \ref{test-2} \ref{test-3} describe the summaries of the experiment results that have been performed with three different alpha values. The result is on all test cases, IS2 cases to IS4 cases were successfully detected by regression and critical path analysis is appropriate. It's just that for the SI1 case, only the alpha value is 0.1
which can successfully detect the regression and determine the source of the cause of the regression with critical path analysis. Other alpha values cannot detect regression and do not perform critical path analysis.

\pagebreak
\begin{table}[htb]
	\caption{Test Cases}
	\label{testcases}
%	\centering
	\begin{tabular}{|l|l|c|c|l|}
		\hline
		\textbf{ID} &
		\textbf{Service/Function} &
		\multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Extra \\ Latency\end{tabular}}} &
		\multicolumn{1}{l|}{\textbf{User}} &
		\textbf{Description} \\ \hline
		IS1 &
		CheckoutService/PlaceOrder &
		100ms &
		25 &
		Extra latency case \#1 \\ \hline
		IS2 &
		CheckoutService/PlaceOrder &
		250ms &
		25 &
		Extra latency case \#2 \\ \hline
		IS3 &
		CheckoutService/PlaceOrder &
		350ms &
		25 &
		Extra latency case \#3 \\ \hline
		IS4 &
		CheckoutService/PlaceOrder &
		250ms &
		75 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS5 &
		CheckoutService/PlaceOrder &
		250ms &
		150 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS6 &
		CheckoutService/PlaceOrder &
		- &
		25 &
		Extra CPU case \\ \hline
		\multirow{5}{*}{IS7} &
		CheckoutService/PlaceOrder &
		\multirow{5}{*}{250ms} &
		\multirow{5}{*}{25} &
		\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Extra latency case\\ with multiple \\ services\end{tabular}} \\ \cline{2-2}
		&
		ProductCatalog/GetProduct &
		&
		&
		\\ \cline{2-2}
		&
		ProductCatalog/ListProducts &
		&
		&
		\\ \cline{2-2}
		&
		ShippingService/GetQuote &
		&
		&
		\\ \cline{2-2}
		&
		\begin{tabular}[c]{@{}l@{}}RecommendationService/\\ ListRecommendations\end{tabular} &
		&
		&
		\\ \hline
		ES1 &
		All Normal &
		- &
		75 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#1\end{tabular} \\ \hline
		ES2 &
		All Normal &
		- &
		150 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#2\end{tabular} \\ \hline
		ES3 &
		\begin{tabular}[c]{@{}l@{}}Checkout load\\ increased to 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#1\end{tabular} \\ \hline
		ES4 &
		\begin{tabular}[c]{@{}l@{}}Curency load \\ increased to 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#2\end{tabular} \\ \hline
	\end{tabular}
\end{table}

@@

\pagebreak

\subsection{Overhead Testing}
Of the 11 test cases, the average PRA Engine tool uses 0.046
vCPU with standard deviation of 0.0038 and 154.41 MiB Memory with standard
deviation of 17.91 in one analysis. The entire cluster has resources
as much as 6 vCPUs and 22.5 GiB, so that in one time doing PRA Engine analysis
resulting in CPU overhead as much as 0.78\% and Memory as much as 0.67\% to the Kubernetes cluster. Overhead caused by the tool is low so that the use of PRA Engine tools will have no impact on the overall performance of the Kubernetes cluster. Tab. \ref{overhead-tbl} shows the result of the overhead testing.
\begin{table}[!htb]
	\caption{Overhead testing result}
	\label{overhead-tbl}
	\centering
	\begin{tabular}{|l|c|c|}
		\hline
		\multicolumn{1}{|l|}{ID} & \multicolumn{1}{l|}{CPU (vCPU)} & \multicolumn{1}{l|}{Memory (MiB)} \\ \hline
		\textbf{IS1}     & 0,042 & 137,82  \\ \hline
		\textbf{IS2}     & 0,043 & 128,71  \\ \hline
		\textbf{IS3}     & 0,04  & 131,55  \\ \hline
		\textbf{IS4}     & 0,045 & 146,6   \\ \hline
		\textbf{IS5}     & 0,046 & 153,61  \\ \hline
		\textbf{IS6}     & 0,047 & 152,71  \\ \hline
		\textbf{IS7}     & 0,048 & 152,71  \\ \hline
		\textbf{ES1}     & 0,049 & 168,8   \\ \hline
		\textbf{ES2}     & 0,05  & 183,68  \\ \hline
		\textbf{ES3}     & 0,051 & 176,59  \\ \hline
		\textbf{ES4}     & 0,052 & 165,75  \\ \hline
		\textbf{Average} & 0,046 & 154,411 \\ \hline
		\textbf{STD}     & 0,038 & 17,916  \\ \hline
	\end{tabular}
\end{table}
%\pagebreak

\section{Analysis}
Of all the test cases, the results obtained from the test will be
depending on the significant value used to test each case.
There are 3 significant values that the author uses to perform the test, namely 0.1, 0.005, and 0.001 with the aim of testing the sensitivity of the detection algorithm regressions are given different significant values. The result is a test with
a significant value of 0.1 successfully detects and analyzes the cause of the regression with true in all test cases, but in tests with a significant value of 0.05 and 0.001 SI1 cases were not detected as regression.

>>>>

\documentclass[conference]{configs/IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{listings}
\lstset{
	frame=single,
	basicstyle=\footnotesize,
}

\makeatletter
\def\lst@makecaption{%
	\def\@captype{table}%
	\@makecaption
}
\makeatother

%\def\tablename{Table}
%\def \figurename{Figure}

@@

\begin{abstract}
In applications with Microservice architecture, when a significant change occurs and result in decreased performance or regression, it is difficult to perform analysis to check which part of the whole Microservice is the main cause of the regression due to the distributed nature of Microservice. Distributed tracing can be used to analyze and determine whether there is a regression and the cause of the regression by utilizing latency data from existing operations on Microservice application.
This system will perform performance regression analysis using the distributed tracing tool Zipkin. Regression is then can be detected using Kolmogorov-Smirnov statistical analysis which will compare the latency data samples that occur
periodically and the sample latency baseline data that represents application performance  under normal circumstances. The analysis will compare the Cumulative
Distribution Function (CDF) of the two samples and see if both
CDF comes from a different distribution. If it is found that both CDFs originate from different distributions, it then can be suspected that there has been a performance regression because the distribution of the periodic data has deviated from the distribution of the baseline data.
If a regression is detected, the system will then perform a critical path analysis to see which operations of each services are most likely contributed to the regression. The analysis will be executed by finding the difference
latency of periodic and baseline operation data and it will be seen which operation's latency difference exceeds a predetermined limit.
The performance regression analysis system has been tested on a Microservice application that runs on Kubernetes. The result is that out of 10 out of 11 test cases, and for every successful case, the main suspected operation that causes regression is found. Implementing the system adds an average overhead of 0.78\% CPU usage and 0.67\% Memory usage.
\end{abstract}

@@

For this paper, the performance metric that will be analyzed from the microservice-based application is limited to latency performance only. The latency data is one of the default data provided by several distributed tracing tools, so the performance regression that will be analyzed in this paper is only related to latency of the API calls performed by the services inside the microservice application.

@@

\subsection{Performance Regression Detection in DevOps}
This study \cite{regression-detection} proposes to perform regression detection performance at the DevOps stage, i.e. at the level of the source code change. The main thing considered is to avoid detecting performance regressions after the app is deployed and running in a production environment. There are two ways proposed by the research
to detect performance regressions at the DevOps stage:
\begin{enumerate}
	\item Perform regression detection at the source code level by extracting
	every Git commit and identify which test cases are affected by
	regression on each commit. After that, the performance of each commit will be
	evaluated chronologically using the relevant test cases or
	benchmarks of performance. Finally, a statistical analysis will be executed on the performance evaluation
	to identify which changes resulted in the performance regression. To find out the root of the problem at the code level, an iterative approach will be done  to identify the root causes of
	regression until it can no longer generate new reasons.
	\item Predict which tests may manifest regression at the commit level. This approach is a continuation of the previous point where
	the approach of doing a test on every commit takes a lot
	resources and effort so that this approach will make predictions
	automatically whether a test will manifest a performance regression given a commit code. In detail, this approach will detect whether there is a regression on certain tests of a commit. To make a prediction model, it must first identified which tests are prone to yielding regression by evaluating all the tests affected by the code changes in previous commits by calculating the performance of each test, such as response time,
	CPU and Memory usage, I/O reads and writes, by doing
	each test sequentially.
\end{enumerate}

@@

There are two approaches that can be taken to solve the problem of performance regression \cite{regression-detection}, namely:
\begin{enumerate}
	\item Regression detection is executed after the application has been developed and deployed in a dedicated environment:
	\item Regression detection is executed before the application is developed and deployed, and then conducting a study of the resulting changes to the source code
\end{enumerate}

%Given the distributed nature of Microservices, it will be difficult for developers if regression detection is executed with an individual approach on each existing servce especially when the number of existing servce is very large, and the interdependence relationship between services becomes complicated. Therefore, to overcome performance regression in microservice-based application, an approach that does not require developers to source search is needed. So that in the case of detection and regression analysis of microservice-based application performance, the first approach is more suitable to use.
Given the distributed nature of microservices, it will be difficult for developers if regression detection is executed with an individual approach on each existing service especially when the number of existing service is very large, and the interdependence relationship between services becomes complicated. Therefore, to overcome performance regression in microservice-based application, an approach that does not require developers to source search is needed. With the help of distributed tracing tool, performance related data from multiple services in a distributed microservice-based application can be collected and analyzed in a single collective source, so that the developer should not be worried about analyzing each and every service available to perform regression related problem, rather they can rely on the data provided from the distributed tracing tool to analyze the whole microservice-based application. In the case of detection and regression analysis of microservice-based application performance, the first approach is more suitable to use.

Therefore, the workflow that must be executed by the performance regression analysis (PRA) system is as follows:
\begin{enumerate}
	\item The system must be able to detect when there is a regression in microservice-based application
	\item The system must be able to determine the source or root cause of the regression after it is detected
\end{enumerate}

Seeing the needs of the PRA system above, the approach the will be executed to do performance regression analysis will be Cumulative Analysis and Aggregation Analysis \cite{parker2020distributed}.

Cumulative Analysis is an approach to analyze certain metrics of application such as latency by cummulating all the collected data as a single representation such as Histogram. With this approach, the distributed nature of many services in microservice-based application can be observed as a single figure or representation so that the whole Microservice application can be monitored in a single space. To use this approach, all the latency data acquired from the distributed tracing will be collected and converted into a Cumulative Distribution Function (CDF). Cumulative Distribution Function is a function whose value is the probability that a corresponding continuous random variable has a value less than or equal to the argument of the function. This statistical function is useful to represent a set of corresponding data into a single quantifiable function which can be useful as a comparison tool.

One of the available tool to analyze and compare large sets of data is called Kolmogorov-Smirnov (K-S) statistic test. The K-S statistic test will count the difference between two CDFs as a scalar number \cite{kolmogorov_1951}. K-S statistic are obtained by finding the furthest vertical distance between the two CDFs as indicated by the arrows. The greater the distance, the more likely it is that two CDFs are from two different distributions so that it can be an indication that there has been a change on pattern of the data represented, for example the latency performance of a microservice-based application.
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.35\textwidth]{resources/ch2/ks.png}
	\caption{CDF of two samples, arrows indicate the Kolmogorov-Smirnov statistical value \cite{wiki:ks-test}}
	\label{ks-example}
\end{figure}

@@

Listing \ref{ks-code} is a sample implementation of the Cumulative Analysis using Kolmogorov-Smirnov test in Python language.
\lstinputlisting[language=Python,caption={Kolmogorov-Smirnov statistic test Algorithm}, label={ks-code}]{codes/ch4/ks.py}

The Cumulative Analysis approach will be used to fullfil the first needs of the PRA system by using Kolmogorov-Smirnov statistic test.

@@

Tab. \ref{aggregate} shows the result of the Aggregation Analysis approach which will be useful in determining the possible root cause of the regression by comparing the latency performance of multiple operations in several services. This approach will be used to fullfil the second needs of the PRA system.
\begin{table}[!htb]
	\caption{Aggregation Analysis result}
	\label{aggregate}
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		\textbf{Service/Operation} & \textbf{Baseline} & \textbf{Regression} & \textbf{Difference} \\ \hline
		inventory/write-cache & 63.1 ms & 368 ms  & +305 ms  \\ \hline
		inventory-db/update   & 1.75 ms & 2.26 ms & +0.51 ms \\ \hline
		memcached/set         & 4.94 ms & 4.71 ms & -0.23 ms \\ \hline
		inventory/update      & 15.2 ms & 14.8 ms & -0.47 ms \\ \hline
		inventory/db-update   & 32 ms   & 30.6 ms & -1.4 ms  \\ \hline
	\end{tabular}
\end{table}
\pagebreak

Fig. \ref{flow-pra} illustrates the phases to be executed by the PRA system. In general, there will be two phases to be executed, namely the baseline loading phase
and the periodic analysis phase. The first phase, namely the loading phase, will look for stable application activity data that can be used as a baseline or a reference for the analysis to be executed in the next stages. This application activity data can be acquired by observing a period of the microservice application that can be considered as a normal or stable activity. For example we can extract latency data from the distributed tracing tool for a period of one day that can represent the entirety of the stable latency performance that can be used in the next phases as our baseline performance data. This phase will produce two artifacts, the latency data of all recorded traces by the tracing system, and operating data that occurs on the critical path of all traces along with its latency value which will be stored as a key-value pair as well.
\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.45\textwidth,scale=5]{resources/ch3/alur_v2.png}
	\caption{PRA system workflow}
	\label{flow-pra}
\end{figure}

The next phase is the periodical analysis phase. This phase will run continuously and the analysis will be run periodically at intervals of every 5 minutes or however long the developer wants the interval to be. This is executed to continuously detect whether there is a regression and
immediately determine the source of the regression if it occurs. There are several stages of analysis to be executed in this phase. The first analysis stage will compare the results transformation of data latency of all ongoing traces periodically with the baseline latency artifact from the loading phase. The comparison will be made within a certain period. The comparison of the two latency data will produce Kolmogorov-Smirnov statistic. If the Kolmogorov-Smirnov statistic that is generated indicates that the two samples of latency data come from two different distributions, then it can be an indication that there has been a regression in the data capture in the periodical phase.

@@

There are two stages that will be executed to do this experiment test, the first is baseline data collection stage. Baseline data will be taken by simulating
the usage of the application by using the Load Generator which will run with variable of \textbf{25 Users} and \textbf{5 Spawn Rates} for \textbf{1 hour}. This baseline data will then be stored by the engine for use in future test cases. The next step is to carry out experiment testing with cases which will be explained in more detail further.

There are two types of test cases to be tested on the system. Tirst type are cases that simulate regression by making changes that occurs at the application level by making modifications intentionally at the code level.
The first case will have an ID with an \textbf{IS} prefix signifying the \textit{Internal-Scenario}.
The second type are cases that simulate regression by increasing the number of users and load on the Load Generator. The second case will have an ID with the \textbf{ES} prefix denotes an \textit{External-Scenario}. Tab. \ref{testcases} will explain the test cases in detail.

@@

\subsection{Experiment Result}
The following tables \ref{test-1}, \ref{test-2}, and \ref{test-3} describe the summaries of the experiment results that have been performed with three different alpha values. The result is on all test cases, IS2 cases to IS4 cases were successfully detected by regression and critical path analysis is appropriate. It's just that for the SI1 case, only the alpha value is 0.1
which can successfully detect the regression and determine the source of the cause of the regression with critical path analysis. Other alpha values cannot detect regression and do not perform critical path analysis.

\begin{table}[htb]
	\caption{Test Cases}
	\label{testcases}
%	\centering
	\begin{tabular}{|l|l|c|c|l|}
		\hline
		\textbf{ID} &
		\textbf{Service/Function} &
		\multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Extra \\ Latency\end{tabular}}} &
		\multicolumn{1}{l|}{\textbf{User}} &
		\textbf{Description} \\ \hline
		IS1 &
		Checkout/PlaceOrder &
		100ms &
		25 &
		Extra latency case \#1 \\ \hline
		IS2 &
		Checkout/PlaceOrder &
		250ms &
		25 &
		Extra latency case \#2 \\ \hline
		IS3 &
		Checkout/PlaceOrder &
		350ms &
		25 &
		Extra latency case \#3 \\ \hline
		IS4 &
		Checkout/PlaceOrder &
		250ms &
		75 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS5 &
		Checkout/PlaceOrder &
		250ms &
		150 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS6 &
		Checkout/PlaceOrder &
		- &
		25 &
		Extra CPU case \\ \hline
		\multirow{5}{*}{IS7} &
		Checkout/PlaceOrder &
		\multirow{5}{*}{250ms} &
		\multirow{5}{*}{25} &
		\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Extra latency case\\ with multiple \\ services\end{tabular}} \\ \cline{2-2}
		&
		ProductCatalog/GetProduct &
		&
		&
		\\ \cline{2-2}
		&
		ProductCatalog/ListProducts &
		&
		&
		\\ \cline{2-2}
		&
		ShippingService/GetQuote &
		&
		&
		\\ \cline{2-2}
		&
		\begin{tabular}[c]{@{}l@{}}RecommendationService/\\ ListRecommendations\end{tabular} &
		&
		&
		\\ \hline
		ES1 &
		All Normal &
		- &
		75 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#1\end{tabular} \\ \hline
		ES2 &
		All Normal &
		- &
		150 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#2\end{tabular} \\ \hline
		ES3 &
		\begin{tabular}[c]{@{}l@{}}Checkout load\\ increased to 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#1\end{tabular} \\ \hline
		ES4 &
		\begin{tabular}[c]{@{}l@{}}Curency load \\ increased to 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#2\end{tabular} \\ \hline
	\end{tabular}
\end{table}

@@

%\pagebreak

\subsection{Overhead Testing}
Of the 11 test cases, the average PRA Engine tool uses 0.046
vCPU with standard deviation of 0.0038 and 154.41 MiB Memory with standard
deviation of 17.91 in one analysis. The entire cluster has resources
as much as 6 vCPUs and 22.5 GiB, so that in one time doing PRA Engine analysis
resulting in CPU overhead as much as 0.78\% and Memory as much as 0.67\% to the Kubernetes cluster. Overhead caused by the tool is low so that the use of PRA Engine tools will have no impact on the overall performance of the Kubernetes cluster. Tab. \ref{overhead-tbl} shows the result of the overhead testing.
\begin{table}[!htb]
	\caption{Overhead testing result}
	\label{overhead-tbl}
	\centering
	\begin{tabular}{|l|c|c|}
		\hline
		\multicolumn{1}{|l|}{ID} & \multicolumn{1}{l|}{CPU (vCPU)} & \multicolumn{1}{l|}{Memory (MiB)} \\ \hline
		\textbf{IS1}     & 0,042 & 137,82  \\ \hline
		\textbf{IS2}     & 0,043 & 128,71  \\ \hline
		\textbf{IS3}     & 0,04  & 131,55  \\ \hline
		\textbf{IS4}     & 0,045 & 146,6   \\ \hline
		\textbf{IS5}     & 0,046 & 153,61  \\ \hline
		\textbf{IS6}     & 0,047 & 152,71  \\ \hline
		\textbf{IS7}     & 0,048 & 152,71  \\ \hline
		\textbf{ES1}     & 0,049 & 168,8   \\ \hline
		\textbf{ES2}     & 0,05  & 183,68  \\ \hline
		\textbf{ES3}     & 0,051 & 176,59  \\ \hline
		\textbf{ES4}     & 0,052 & 165,75  \\ \hline
		\textbf{Average} & 0,046 & 154,411 \\ \hline
		\textbf{STD}     & 0,038 & 17,916  \\ \hline
	\end{tabular}
\end{table}
%\pagebreak
%
\section{Analysis}
Of all the test cases, the results obtained from the test will be
depending on the significant value used to test each case.
There are 3 significant values that the author uses to perform the test, namely 0.1, 0.005, and 0.001 with the aim of testing the sensitivity of the detection algorithm regressions are given different significant values. The result is a test with
a significant value of 0.1 successfully detects and analyzes the cause of the regression with true in all test cases, but in tests with a significant value of 0.05 and 0.001 SI1 cases were not detected as regression.
